Indirect elicitation as a necessary condition for consistent surrogate losses\jessie{Change this as we reframe??}

### 2020-12-10 colt-21/cvx-flats.tex
Meeting Notes 10 Dec 20

\section{Introduction}\label{sec:intro}

%supervised learning blah
Surrogate risk minimization is one of the most widespread techniques in supervised machine learning.
%A surrogate loss is often necessary for one of two reasons: (1) the target loss does not satisfy some desiderata, such as convexity, or (2) the target loss may not be given at all, as is often the case in continuous estimation problems, when one instead has a target conditional statistic to estimate from training data.
Often, we desire surrogate losses to be \emph{consistent}, as this precedes deriving excess risk bounds and rates.
Roughly speaking, consistency means that minimizing surrogate risk corresponds to solving the target problem of interest:
the target risk should also be minimized, or the average deviation to the true conditional statistic function converges to 0.\jessie{Not sure if I like these sentences here, or in general}

@@

\subsection{Consistency} \label{subsec:consistency}
\jessie{Looking at this now, sections 2.1-4 feel like a lot...}
\jessie{I think the story we want to tell is as follows: there are these two types of problems where [convex] prediction dimension is important.  Typically, these problems are studied with different tools; here, we present a tool to bound prediction dimension in both settings.  This tool relies on property elicitation, which we show (somehow for the first time to our knowledge) can be formally connected to consistency.}

@@

@@

We now state our elicitation lower bound, which when combined with Theorem \ref{thm:consistent-implies-indir-elic}, implies consistency bounds.
A similar result is \citet[Theorem 9]{agarwal2015consistent}, which bounds the dimension of level sets of a single-valued $\prop{L}$.
Theorem \ref{thm:cvx-flats} instead bounds the dimension of flats contained in the level sets, an additional power which we leverage in our examples.
Theorem \ref{thm:cvx-flats} also gives a lower bound for any given target $\ell$ or $\gamma$, rather than a given surrogate $L$.
\raf{Cut the last bits here; I bet AA15 thought of their result as being about consistency, though I could be wrong}
% (although an analogous implication of their Theorem 9 may have been known to \citet{agarwal2015consistent}).
% We also note that the lower bound on elicitation complexity in \citet{agarwal2015consistent} is not translated into a lower bound for \emph{consistent} surrogates, which is the main contribution of this work.

>>>>

\section{Introduction}\label{sec:intro}
\jessie{Without moving anything around, take a shot at storyboarding this.  Want enough detail to understand how much time to spend on each chunk.  (1 bullet per paragraph)}
\jessie{Could be handy to have Han's paper in here.  Play down some of the continuous value examples.}
%supervised learning blah
Surrogate risk minimization is one of the most widespread techniques in supervised machine learning.
%A surrogate loss is often necessary for one of two reasons: (1) the target loss does not satisfy some desiderata, such as convexity, or (2) the target loss may not be given at all, as is often the case in continuous estimation problems, when one instead has a target conditional statistic to estimate from training data.
Often, we desire surrogate losses to be \emph{consistent}, as this precedes deriving excess risk bounds and rates.
Roughly speaking, consistency means that minimizing surrogate risk corresponds to solving the target problem of interest:
the target risk should also be minimized, or the average deviation to the true conditional statistic function converges to 0.\jessie{Not sure if I like these sentences here, or in general}

@@

\subsection{Consistency} \label{subsec:consistency}
\jessie{Looking at this now, sections 2.1-4 feel like a lot...}
\jessie{I think the story we want to tell is as follows: there are these two types of problems where [convex] prediction dimension is important.  Typically, these problems are studied with different tools; here, we present a tool to bound prediction dimension in both settings.  This tool relies on property elicitation, which we show (somehow for the first time to our knowledge) can be formally connected to consistency.}
\jessie{Could split into high level in previous work; ie previous work and setting are distinct.}
\jessie{Top of 2 in setting}
\jessie{Want a clear distinction between what came before and what we're adding.}
\jessie{Can defer Lemma 8 to appendix?  Maybe}

@@

\jessie{Simplify; merge with Sec 4.  Jessie take a pass at proof sketch of Theorem 1}

@@

We now state our elicitation lower bound, which when combined with Theorem \ref{thm:consistent-implies-indir-elic}, implies consistency bounds.
\jessie{Be explicit about corollary; add corollary after Thm 11.}
A similar result is \citet[Theorem 9]{agarwal2015consistent}, which bounds the dimension of level sets of a single-valued $\prop{L}$.
Theorem \ref{thm:cvx-flats} instead bounds the dimension of flats contained in the level sets, an additional power which we leverage in our examples.
Theorem \ref{thm:cvx-flats} also gives a lower bound for any given target $\ell$ or $\gamma$, rather than a given surrogate $L$.
\raf{Cut the last bits here; I bet AA15 thought of their result as being about consistency, though I could be wrong}
% (although an analogous implication of their Theorem 9 may have been known to \citet{agarwal2015consistent}).
% We also note that the lower bound on elicitation complexity in \citet{agarwal2015consistent} is not translated into a lower bound for \emph{consistent} surrogates, which is the main contribution of this work.
